---
title: "Making .pdf Files (Sample)"
author: "PPOL 6803-03"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

#install.packages("tinytex")
#tinytex::install_tinytex()
```

Here we want to show how to make .pdfs using R Markdown. Fortunately, it's fundamentally the same as making .html files -- we just have to swap out our output type!  

Just like in .html files, there are a few fun features we can do in the "text" portion of Markdown. For example, we can add footnotes^[Such as the footnote here!] and also add hyperlinks. We can add hyperlinks to external websites like [this](www.google.com), by including any website url like http://ppol_6803.alexanderpodkul.com/syllabus.html, and by referencing different parts of this document such as [Splitting Data]! 

- We can also 
- Create bullet points
- Like this

or we can create numbered lists like

1. list
2. can go 
3. here


## Header 
Section introduction text can go here

### Sub-Heading Example

Here we can include code if we want:

```{r, echo = T, eval = T, message=F, warning=F}
library(dplyr)

url <- 'https://raw.githubusercontent.com/apodkul/ppol6803_03/main/Data/life_expect.csv'
ctry_data <- read.csv(url)

ctry_data %>% 
  glimpse()

```

### Another Sub-Heading Example

Or we can include the code output, without the code: 

```{r, echo = F, eval = T, message=F, warning=F}
library(ggplot2)

ggplot(ctry_data, aes(x = Population)) + 
  geom_histogram(fill = 'gray', color = 'navy') + 
  scale_x_log10(labels = scales::label_log()) + 
  ggthemes::theme_stata() + 
  labs(title = 'Title can go here', 
       subtitle = 'Subtitle can go here', 
       caption = 'Data source: Wherever Prof. Podkul found this')
```




