---
title: "Title"
author: "Author"
date: "04/12/2023"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview 

While there are others, I recommend using one of the three following presentation formats. (Note: You can change the format in the `output` parameter in the header of the `.rmd` file.)

- `beamer_presentation` for making .pdf slides (using a .tex engine)
- `ioslides_presentation` for making .html files 
- `slidy_presentation` for making .html files

## Syntax

The syntax for R Markdown slides is similar to creating R Markdown documents (like problem sets).

We can write sentences using __bold face__, _italics_, using [links](http://ppol670.alexanderpodkul.com) or also make equations like 

$$ x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}$$

We can also (Note: replace with - for unnumbered): 

1. write 
2. numbered 
3. lists 



## Syntax (Continued)

We can also continue to write code. 

```{r, echo=T}
example_code <- 'This will be printed'
```

```{r, echo = F}
example_code2 <- 'This will not be printed'
```

Remember, in the header to the code chunk:

- `echo` - TRUE/FALSE - will printthe code in our output
- `eval` - TRUE/FALSE - will _evaluate_ the code chunk 
- `warning` - TRUE/FALSE - will print any warnings that the code produces
- `message` - TRUE/FALSE - will print any messages that the code produces

(or set globally in line 9)

## Creating New Slides 

The only major difference is that `## Title` creates a new slide in our deck(!)  

## Adding Visualizations 

```{r, echo = F, eval=T, fig.align='center', out.height='90%', out.width='90%'}
library(ggplot2)
library(ggthemes)
data <- data.frame(x = 1:500, 
                   y = rnorm(n = 500, mean = 10, sd = 30)
                   )

ggplot(data) + 
  geom_density(aes(x = y)) + 
  theme_igray()

```


## Common Pitfalls and Advice

__Common Pitfalls__

- Having stray spaces (in slide names or in lists)
- Re-running timely models every time you "knit"
- Forgetting to start a new slide


__Advice__

- When starting out, __Knit__ after each slide is done (to isolate errors)
- Only include the data and code that you need
- Run code chunk by chunk to isolate errors


## Resources 

Useful documentation: 

- [R Markdown Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) 
- [ioslides Documentation](https://bookdown.org/yihui/rmarkdown/ioslides-presentation.html)
- [Slidy Documentation](https://bookdown.org/yihui/rmarkdown/slidy-presentation.html)
- [beamer Documentation](https://bookdown.org/yihui/rmarkdown/beamer-presentation.html)


Additional customization: 

- [Using beamer](https://bookdown.org/yihui/rmarkdown/beamer-presentation.html#themes)
- [Using Slidy](https://garrettgman.github.io/rmarkdown/slidy_presentation_format.html#appearance_and_style)
- [Using ioslides](https://bookdown.org/yihui/rmarkdown/ioslides-presentation.html#custom-templates-2)
